Supplement

### 2023-07-05 paper/manuscript.Rmd
small text fixes

@@

[TODO This is good but could use more build-up. Something like. In practice, most scientific work is not conducted under such ideal conditions. Studies are generally run by graduate students with limited budgets ... . Therefore, an important question to ask is how replicable findings in the literature are for graduate students operating under less-than-ideal conditions.]

In practice, most scientific work is not conducted 
Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science. If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either. Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts [@frank2012]. Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original [@mathur2020].

[TODO possibly say more??]

@@

[TODO is there a citation for experimental design features being possibly relevant?]

@@

[Awkward transition]

However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications. As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.

@@

Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020]. We calculated how often the original and replication results were distributionally consistent. If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in @olsson2020 (tau=.21 in SMD units), then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replications are distributionally consistent with the original. More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.

[what was I supposed to say about heterogeneity, and is this the right place for it?]

@@

TODO any citations around experimental design predictors??

Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data. Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and replication switched to online.

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior [@carvalho09]. We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results. Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models. The strongest predictors for prediction interval were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).

```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in red) and a model of all pairs with full statistical information (N=112, shown in blue) and predicting subjective replication scores as the dependent variable. "}

@@

[TODO should we discuss the need for more replications and pooling and coding??]

>>>>

## Large-scale replication projects

@@

In practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts. Therefore, an important question is how replicable findings in the literature are for graduate students operating under these less-than-ideal conditions. If students cannot replicate a finding under these circumstances, it is unlikely that they will be able to successfully build upon the study in these circumstances either.

Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science, by looking for markers of findings that do (or do not) support replication by graduate students operating under typical real-word constraints. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work. In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original [@mathur2020].

## Predicting replication success

@@

@@

While they don't incur the expense of collecting new datasets, correlational approaches do depend on previously collected replication data, and their conclusions are limited by the available data. Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points. In particular, the RP:P dataset is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in RP:P. More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.

@@

Some multi-site replication projects have found heterogeneity in effect sizes across replication sites [@ebersole2020; @klein2018; @olsson2020]. If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in @olsson2020 (tau=.21 in SMD units), then `r round(tau_pct,1)`% (`r tau_predIntcount`/`r tau_predInttotal`) of replication effect sizes are distributionally consistent with the original effect size. More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.

[Is this the right place to talk about heterogeneity / what did we want to say?]

@@

Many predictors individually correlated with subjective replication success (Table \ref{tab:cor}). Predictors of higher replicability included within-subjects designs, larger numbers of trials per subject, and the original study having open data. Predictors of lower replicability included single vignetted studies with only one induction or example per condition, social psychology studies, and original-replication pairs where the original study was in-person and the replication switched to online.

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior [@carvalho09]. We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results. Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (See Supplement for plots of coefficients for these additional models). The strongest predictors for prediction interval were still within-subjects designs (`r within_2`) and studies with larger effect sizes (`r smd_2`).

```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in blue) and a model of all pairs with full statistical information (N=112, shown in red) and predicting subjective replication scores as the dependent variable. "}

@@

### 2023-07-05 paper/manuscript.tex
small text fixes

Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts (ex. terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al. 2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al. 2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result. As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none.

To identify studies are risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability. Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.

{[}Prior paragraph may still need work{]}

@@

While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al. 2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al. n.d.}). Further, the methods for estimating this quantity have been theoretically problematic. Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns. These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole. Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al. 2020}). The importance of a study being replicable is not uniformly distributed across the literature.

{[}Prior paragraph is a bit verbose, but it's probably fine{]}

Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures. With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab. Many Labs looked at which well-known two conditions studies replicate with huge samples, and Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement. All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.

{[}TODO This is good but could use more build-up. Something like. In practice, most scientific work is not conducted under such ideal conditions. Studies are generally run by graduate students with limited budgets \ldots{} . Therefore, an important question to ask is how replicable findings in the literature are for graduate students operating under less-than-ideal conditions.{]}

Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science. If a study cannot be replicated in a given set of circumstances, we believe it it unlikely that the study can be successfully built upon in those circumstances either. Thus, we look at what studies are replicable under the circumstances where most scientific work is conducted: by students who are working with limited budgets, limited time, and without access to outside experts (\protect\hyperlink{ref-frank2012}{Frank \& Saxe 2012}). Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).

{[}TODO possibly say more??{]}

@@

{[}TODO is there a citation for experimental design features being possibly relevant?{]}

@@

{[}Awkward transition{]}

However, while they don't incur the expense of collecting new datasets, correlational approaches depend on data from replications. As large-scale replications are arduous and expensive to run, analyses generally draw heavily on same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.

@@

Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{Klein et al. 2018}, \protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}, \protect\hyperlink{ref-olsson2020}{Olsson-Collentine et al. 2020}). We calculated how often the original and replication results were distributionally consistent. If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al. (\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replications are distributionally consistent with the original. More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replications.

{[}what was I supposed to say about heterogeneity, and is this the right place for it?{]}

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al. 2009}). We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results. Due to a large number of predictors coupled with a small and noisy dataset there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models. The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).

\begin{figure}[ht]
\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in red) and a model of all pairs with full statistical information (N=112, shown in blue) and predicting subjective replication scores as the dependent variable. }\label{fig:mod-results}
\end{figure}

@@

{[}TODO should we discuss the need for more replications and pooling and coding??{]}

>>>>

Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts (ex. terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al. 2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al. 2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result. As each failed extension does not directly contradict the original result, many scientists may waste considerable time and resources pursuing results where there may be none.

To identify studies at risk for non-cumulative findings, we might want to know 1) what to measure in order to capture the waste and frustration due to non-cumulative failed extensions and 2) from a descriptive perspective, what features of studies are associated with being at risk for this non-replicability. Measuring replicability has been the focus of much prior work, but there is limited consensus on what exactly is being estimated.

\hypertarget{large-scale-replication-projects}{%
\subsection{Large-scale replication projects}\label{large-scale-replication-projects}}

@@

While their sampling and methods varied, these previous approaches to replicability have focused on interpreting their results in terms of a potentially problematic estimand: the probability of a finding in the literature being somehow truly replicable. Critics have pointed out that ``true'' replicability may not be possible to estimate outside of a specific sample (\protect\hyperlink{ref-vanbavel2016}{Van Bavel et al. 2016}) or even time period (\protect\hyperlink{ref-ramscar}{Ramscar et al. n.d.}). Further, the methods for estimating this quantity have been theoretically problematic. Sampling schemes did not reflect an entirely random sample from the literature; instead replication projects sampled from specific journals where results may be of more interest and adjusted the sample for feasibility concerns. These are reasonable sampling choices, but they undermine the claim that the estimand is the level of ``truth'' in the literature as a whole. Sampling truly at random from the literature may not even be desirable, as arguably a literature will succeed if useful discoveries come out of it, not if random findings are true (\protect\hyperlink{ref-wilson2020}{Wilson et al. 2020}).

Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methodologies and outcome measures. With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab. Many Labs looked at which well-known two condition studies replicate with huge samples, and Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement. All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.

In practice, most scientific work is conducted by graduate students with limited time, limited budgets and limited access to experts. Therefore, an important question is how replicable findings in the literature are for graduate students operating under these less-than-ideal conditions. If students cannot replicate a finding under these circumstances, it is unlikely that they will be able to successfully build upon the study in these circumstances either.

Our goal in estimating replicability is to look for markers of when findings can (and cannot) support cumulative science, by looking for markers of findings that do (or do not) support replication by graduate students operating under typical real-word constraints. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. Our primary estimand is whether a student researcher, on selecting a finding of interest from the literature, can successfully achieve a result close enough to the original that they could build on it in their own work. In addition to this subjective measure of replicability, we also compare the effect sizes of the original and replication on one key outcome per study using prediction interval and p-original (\protect\hyperlink{ref-mathur2020}{Mathur \& VanderWeele 2020}).

\hypertarget{predicting-replication-success}{%
\subsection{Predicting replication success}\label{predicting-replication-success}}

@@

@@

While they don't incur the expense of collecting new datasets, correlational approaches do depend on previously collected replication data, and their conclusions are limited by the available data. Large-scale replications are arduous and expensive to run, so only a few large-scale replication datasets exist, and most analyses analyses draw heavily on same small set of data points. In particular, the RP:P dataset is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in RP:P. More replication data is needed to identify markers of replicability and targets for potential future experimental approaches.

@@

Some multi-site replication projects have found heterogeneity in effect sizes across replication sites (\protect\hyperlink{ref-klein2018}{Klein et al. 2018}, \protect\hyperlink{ref-ebersole2020}{Ebersole et al. 2020}, \protect\hyperlink{ref-olsson2020}{Olsson-Collentine et al. 2020}). If we assume that the level of heterogeneity in hypothetical multi-site replications of these effects would be the same as the average level heterogeneity found in Olsson-Collentine et al. (\protect\hyperlink{ref-olsson2020}{2020}) (tau=.21 in SMD units), then 64.3\% (72/112) of replication effect sizes are distributionally consistent with the original effect size. More work on understanding heterogeneity is needed to understand what levels of heterogeneity to expect across different implementations of the same experiment, and how considerations of heterogeneity should impact interpretations of both novel results and replication results.

{[}Is this the right place to talk about heterogeneity / what did we want to say?{]}

@@

While a number of predictors show individual correlations with the subjective replication score, many of the predictors intercorrelate with one another. In order to determine which predictors were the strongest, we ran a series of pre-registered regression models regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al. 2009}). We ran both 1) models using all the original-replication pairs, but without original effect size and original p value as predictors, as they were uncodable for some pairs, and 2) models including all predictors, but on only the subset of data where all predictors were available. The coefficient estimates from two models predicting the subjective replication scores are shown in Figure \ref{fig:mod-results}; see Supplement for full model results. Due to a large number of predictors coupled with a small and noisy dataset, there is much uncertainty around the coefficients even with strong regularization. The general directions of coefficients are consistent with the effects of the predictors in isolation.

@@

We also ran models predicting our secondary outcome measures: whether the replication effect was within the prediction interval of the original effect and what the p-original was between the replication and original. Both these models had even more uncertain estimates. While the credible intervals were wide, the general patterns of predictor direction and relative strength were similar to the subjective replication models (See Supplement for plots of coefficients for these additional models). The strongest predictors for prediction interval were still within-subjects designs (0.62, CrI= {[}-0.18, 2.01{]}) and studies with larger effect sizes (0.3, CrI= {[}-0.29, 0.94{]}).

\begin{figure}[ht]
\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Coefficients and uncertaintly estimates from a model of all original-replication pairs (N=176, shown in blue) and a model of all pairs with full statistical information (N=112, shown in red) and predicting subjective replication scores as the dependent variable. }\label{fig:mod-results}
\end{figure}

@@

### 2023-07-05 paper/supplement.Rmd
small text fixes

# Forest plot

@@

# Additional model results
```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) 
}

>>>>

@@

```{r}
do_draws <- function(model){
  draws <- model |> gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> 
    mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |>  filter(Term!="Intercept") |> 
    mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss","z_log_p","z_target_d_calc"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "P-value", "Original effect size"))) 
}
